Testing atlantisom: true biomass output from Atlantis

### 2019-05-21 Atlantisom2SSworkflowtest.Rmd
dont eval lf
need SS ref

On this page we demonstrate use of atlantisom on the California Current output files to provide inputs for a stock assessment model implemented in Stock Synthesis [@SSREF].

@@

```{r lengthcomp-wtage}

>>>>

On this page we demonstrate use of atlantisom on the California Current output files to provide inputs for a stock assessment model implemented in Stock Synthesis [insert SSREF].

@@

```{r lengthcomp-wtage, eval=FALSE}
